### 2022-10-05 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@c82bda2d4fbf4257add2e0471edd1854dc7d2abc 🚀
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@5b2b1da7cfed18eccd4e53e14d47ee8a4f61b83e 🚀

We tested our analytical MaxEnt model against open food-web data queried
from three different sources and integrated into what we call our
\emph{complete dataset}. These sources include (1) terrestrial and
aquatic food webs sampled globally and archived on the ecological
interactions database Mangal; (2) freshwater stream food webs from New
Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan, United
States). First, all food webs archived on \texttt{mangal.io} (Poisot et
al. 2016; Banville, Vissault, and Poisot 2021) were directly queried
from the database (\(N = 235\)). Most ecological networks archived on
Mangal are multilayer networks, i.e.~networks that describe different
types of interactions. We kept all networks whose interactions were
mainly of predation and herbivory types, and removed the largest network
(\(S = 714\)) for computational efficiency reasons. Then, to this set we
added food webs from two different sources: the New Zealand dataset
(\(N = 21\); J. P. Pomeranz et al. 2018) and the Tuesday Lake dataset
(\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our complete dataset
thus contained a total of \(257\) food webs. All code and data to
reproduce this article are available at the Open Science Framework. Data
cleaning, simulations and analyses were conducted in Julia v1.6.1.

>>>>

We tested our analytical MaxEnt model against open food-web data queried
from three different sources and integrated into what we call our
\emph{complete dataset}. These sources include (1) terrestrial and
aquatic food webs sampled globally and archived on the ecological
interactions database Mangal; (2) freshwater stream food webs from New
Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan, United
States). First, all food webs archived on \texttt{mangal.io} (Poisot et
al. 2016; Banville, Vissault, and Poisot 2021) were directly queried
from the database (\(N = 235\)). Most ecological networks archived on
Mangal are multilayer networks, i.e.~networks that describe different
types of interactions. We kept all networks whose interactions were
mainly of predation and herbivory types, and removed the largest network
(\(S = 714\)) for computational efficiency reasons. Then, to this set we
added food webs from two different sources: the New Zealand dataset
(\(N = 21\); J. P. Pomeranz et al. 2018) and the Tuesday Lake dataset
(\(N = 2\); Cohen, Jonsson, and Carpenter 2003). Our complete dataset
thus contained a total of \(257\) food webs. All code and data to
reproduce this article are available at the Open Science Framework
(OSF.IO/KT4GS). Data cleaning, simulations and analyses were conducted
in Julia v1.8.0.
